
\chapter{FUN Boom Tournament}
\begin{quote}
A tournament can be a great deal of fun,\\
  But they’re not meant for everyone.\\
I’ll be back next year at this time,\\
  ’Cause it’s not winning that counts,\\[5 pt]
-- But the friends that you find.\\
\footnotesize \textit{Bud Pell}
\end{quote}
 \newpage
 
These rules are drawn up in order to put the FUN back into boomerang tournaments.

\section{General FUN Boom Tournament Rules}
\begin{enumerate}
\item No competition can start or be said to be valid without a round of Team Ben Ruhe Has a Posse (TBRHAP). At start of each tournament day, one round of TBRHAP must be completed.
\item No general warm up is allowed.
\item Any warm up for ordinary (boring) events must be in the form of a FUN game.
\item FUN games are scored separately and count for nothing at all, but to have FUN. If no FUN has been had during the FUN game, another FUN game must be completed before the ordinary event can start.
\end{enumerate} 
 
\section{Event FUN Boom Rules}
\begin{enumerate}
\item The FUN game before Accuracy can be Team Hackuracy or Team Accuracy.
\item The FUN game before Fast Catch can be Team Fast Catch.
\item The FUN game before Endurance can be Team Fast Catch.
\item The FUN game before Aussie Round can be Super Mario Brothers.
\item The FUN game before MTA can be Suicide MTA.
\item The FUN game before Trick Catch can be GLORP.
\item Long Distance isn’t FUN.
\end{enumerate} 
 
\section{FUN Games Rules}
\subsection{Team Ben Ruhe Has a Posse}
All participants, their friends and families join in for a suicide throw. Everybody throws at the same time, and all who catch are documented by name. The winner can be mentioned on the field and given three cheers.
Only one attempt must be made each day of the tournament.

\subsection{Team Hackuracy}
Each member of the team in turn throws a boomerang and the whole team helps hacky (kick) the boomerang toward the bull’s eye. The number of hackies is added to the score.

\subsection{Team Accuracy}
Each member of the team in quick successive turns throws a boomerang such that the next thrower throws before the previous has landed. This means, that the whole team must be ready to go in line. As ordinary Accuracy rules apply, no boomerang must be touched by anyone on the team until it has been scored, so watch out for all those incoming boomerangs while you’re busy throwing your own before the previous one has landed! When all boomerangs have landed, the four best scores are counted and added to the total score.

\subsection{Team Fast Catch}
Two teams are made from all available persons on the field. The first thrower of each of the two teams starts throwing at the same time. When the thrower has retrieved his boomerang and touched the bull’s eye he runs out to tag the next thrower ready at the 10-meter line.
Each team must make twenty catches and the one catching number 20 runs to a chair which is set up at equal distance from the two circles. The first team to get a person in the chair wins.

\subsection{Super Mario Brothers}
Everybody throws at the same time. The object is to catch your boomerang in the bull’s eye or as close as possible. The ones catching in the bull’s eye, or if none, the closest to the bull’s eye, get one point. Those who didn’t catch their boomerang get minus three points. The rest get no points. The first person to get 10 points wins. No one can have less than minus three points. If two or more throwers are equally close to the bull’s eye, both are awarded points.
To shorten the game, the minus three points for dropping can be dismissed, and the goal can be set to 3 or 5 points for the winner.

\subsection{Suicide MTA}
Everybody throws at the same time. The last person to catch wins the round.
Five or ten rounds should be enough for warm up.

\subsection{GLORP}
G-L-O-R-P is a freestyle trick catch game. To start with the throwers are ranked according to the number of years they have thrown boomerangs. The first person (the dominator) attempts a trick catch of his own choosing. If he succeeds, all the others must duplicate it, or else get a letter. If the dominator fails to catch the boomerang, the domination is passed to the next one in the ranking line. If the previous dominator caught the boomerang, but missed the trick catch he attempted, the next dominator must catch his boomerang in his attempt, or else he gets a letter. When a thrower has got the five letters G-L-O-R-P he is out of the game. The last person in the game is the winner.
 
 
 
