\section*{Preface}
If you can only own one book about boomerangs - this is the book!
After more than 2 decades this book is still going strong. Now in a new revised digital edition. We have added a digital index, digitized all the drawings, redesigned the whole book and a lot more.
This new version is a relaunch with the community in mind.

Every contribution, will is appreciated. If you have any ideas or corrections for the book, or you want to be a part of the development find me on social media or send an email: dkcookie@gmail.com

Best Regards\\
David Bjerre Børklund\\

\subsection*{Part of the old preface}
When most people hear the word boomerang, the first things that spring to mind are a bent piece of wood and Australia. Today’s boomerangs are, however, quite different from the original shape. More new designs and techniques are currently being developed in Europe and the USA than by the Australian Aboriginees. New shapes, including multibladers are being developed to fly steady, accurate flight patterns. They are made from special plywoods and other hi-tech materials and adjusted by weighting and bending to achieve flights which would not have been considered possible until just a few years ago. There have been significant developments in the '90s that have not been published in boomerang literature.
\par
``The Ultimate Boomerang Book'' is an indispensable adviser for all boomerang freaks and for those who want to be. The book is also being translated into french, japanese and danish. The ``Ultimate Boomerang Book'' adds significantly to the international collection of literature on boomerang making and throwing.